### 2015-08-14 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
Updates in the proposal

The main objectives of this proposal are:
\begin{enumerate}[(i)]
%
   \item Investigation of \CO\; plume dynamics (migration and leakage);
%
   \item \red{Investigation of multi-fluid flows through zones of potential rheological weakness in the overburden (e.g., faults and chimneys): solid-fluid interactions and stress-induced fractures formation;}
%
   \item \red{Model uncertainty quantification: sensor network (data assimilation) and ROM};
%
   \item Model quality assurance
%
\end{enumerate}

>>>>

The main objectives of this proposal are:
\begin{enumerate}[(i)]
%
   \item Investigation of \CO\; plume dynamics (migration and leakage);
%
   \item \red{Investigation of multi-fluid flows through zones of potential rheological weakness in the overburden (e.g., faults and chimneys): solid-fluid interactions and stress-induced fractures formation;}
%
   \item \red{Model uncertainty quantification: sensor network (data assimilation) and ROM};
%
   \item Model quality assurance (monitoring $\&$ verification for risk assessment and environmental impact).
%
\end{enumerate}

{\bf The novelty of this project is in addressing in an integrated way detailed modelling of \CO\; flows under reservoir conditions (plume migration $\&$ leakage), changes on petrophysical properties (permeability/porosity spatial- and time-variability), solid-fluid interactions (integrity of repositories) and monitoring $\&$ verification technologies.} We shall consider multi-scale and multi-physics aspects of CCUS problem: two length-scales:

both the polydispersity and the closure problems by resorting to a self-consistent multiscale modelling approach. We shall consider two (length) scales: a microscopic scale, comparable with the characteristic size of the discrete particles, and a macroscopic scale, comparable with the characteristic length of the gradients that the modeller wishes to capture in the system analysed. We shall employ Lagrangian modelling at the microscale and Eulerian modelling at the macroscale. With the information provided by the Lagrangian simulations, we shall develop constitutive equations that we shall implement in the Eulerian model, experimentally validated for different types of flow by means of advanced imaging techniques (Fig.1). The ultimate goal is to develop a self-standing Eulerian (that is, continuum) model for dense fluid-particle flows, able to correctly describe polydispersity and solvable by means of CFD codes.
